\documentclass{report}

\usepackage{prince2}
\usepackage{hyperref}
\usepackage{color}

\usepackage[T1]{fontenc}
\usepackage{titlesec, blindtext, color}
\definecolor{gray75}{gray}{0.75}
\newcommand{\hsp}{\hspace{20pt}}
\titleformat{\chapter}[hang]{\Huge\bfseries}{\thechapter\hsp\textcolor{gray75}{|}\hsp}{0pt}{\Huge\bfseries}

\begin{document}
\princeplan
\project{Project Name}
\date{\today}
\author{P.Ryzhov}
\client{Client name}
\maketitle

\chapter{Plan History}

\section{Document Location}
This document is only valid on the day it was printed.
The source of the document will be found on the project's PC in location.

\section{Revision History}

Date of this revision: 2016-01-29

\begin{center}
    \begin{tabular}{| p{2cm} | p{2cm} | l | p{2cm} |}
    \hline
    Revision data & Previous revision date & Summary of changes & Changes marked \\
    \hline
    2016-01-29 & & First issue & \\
    \hline
    \end{tabular}
\end{center}

\section{Approvals}
This document requires the following approvals.
Signed approval forms are filed in the Management/Specialist/Quality section of the project files.

\begin{center}
    \begin{tabular}{| p{2cm} | p{2cm} | l | p{2cm} | p{2cm} |}
    \hline
    Name & Signature & Title & Date of Issue & Version \\
    \hline
     & & & & \\
    \hline
    \end{tabular}
\end{center}

\section{Distribution}
This document has been distributed to:

\begin{center}
    \begin{tabular}{| p{2cm} | l | p{2cm} | p{2cm} |}
    \hline
    Name & Title & Date of Issue & Version \\
    \hline
     & & & \\
    \hline
    \end{tabular}
\end{center}

\tableofcontents

\chapter{Plan}

\section{Plan Description}
A brief description of what the plan encompasses (i.e. project, stage, team, exception) and the planning approach.

\section{Plan Prerequisites}
Any fundamental aspects which must be in place, and remain in place, for the plan to succeed.

\section{External Dependencies}
Any external dependencies which may influence the plan.

\section{Planning Assumptions}
Any assumptions upon which the plan is based.

\section{Lessons Incorporated}
Details of relevant lessons from previous similar projects which have been reviewed and accommodated within this plan.

\section{Monitoring and Control}
Details of how the plan will be monitored and controlled.

\section{Budgets}
Covering time and cost, including provisions for risks and changes.

\section{Tolerances}
Time, cost and scope tolerances for the level of plan (it may also include more specific stage or team level risk tolerances).

\section{Product Descriptions}
Covering the products within scope of the plan (for the Project Plan this will be the project product; for the Stage Plan this will be the stage products; and for a Team Plan this will be a reference to the Work Package assigned).  Quality tolerances are defined in each Product Description.

\section{Schedule}

Which may include graphical representations of:
\begin{itemize}
\item Gantt or bar chart 
\item Product breakdown structure (see Appendix D for an example)
\item Product flow diagram (see Appendix D for an example)
\item Activity network 
\item Table of resource requirements --- by resource type (e.g. four engineers, one test manager, one business analyst)
\item Table of requested/assigned specific resources --- by name (e.g. Nikki, Jay).
\end{itemize}

\end{document}